---
title: "HW1_S23"
author: "Shengyuan Wang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
options(scipen = 1, digits = 16)
```


## Homework 1, due Wednesday 1/25 at 5PM 
Homework guidelines: 

- Turn in this assignment as a PDF on Moodle, please! To create a PDF, I suggest knitting to HTML, then opening the HTML file in a browser and saving to PDF from there. 

- You're invited to collaborate and discuss with each other, and then each person should turn in their own assignment, which should be their own work.  "Discussing" is very different from copying and I trust students to stay on the right side of this line. In general, anything you say out loud to another person is fine, and looking at a screen together (in person or on Zoom) is fine. Sharing files or screenshots is a bad idea. Name the people you work with below (question 0). 

- If you start early, you're giving yourself the chance to ask questions and turn in a polished product. If you start late, you won't be able to get help as easily. 

### Q0: Names
Who did you work with on this assignment? You'll get a bonus 5 points if you name someone and they name you. *No scores above 100% are allowed, but these bonus points can repair mistakes on this assignment*.

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px;"}

**Solution**:

Name: Shengyuan Wang

I worked with Wenxuan Zhu on this assignment.

:::

### Q1: Eigenvalues of a symmetric matrix

- Suppose that $A$ is an $n\times n$ matrix and that $x$ is a vector in $\mathbb{R}^n$. Is $x^TAx$ a number, vector, or matrix? 

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px;"}

**Solution**:

$x^T$ is a $1 \times n$ vector, $A$ is a $n \times n$ matrix, $x$ is a $n \times 1$ vector.
So when they time together, the result $x^TAx$ will be a number.

:::



- Suppose that $Ax = \lambda x$ and $A = A^T$ and $x$ is not all zeros; that is, $\lambda$ is an eigenvector of a symmetric matrix $A$ with eigenvalue $\lambda$. Show that $x^TAx = \lambda x^Tx$. Explain why this means that $\lambda$ must be a real number. 

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px;"}

**Solution**:

Since $A$ is real, $\overline{A} = A$, $\overline{A}$ here is the element-wise complex conjugate. 
\[A\overline{x} = \overline{\lambda}\overline{x}\]
Then, we can transpose both side adn we will get 
\[\overline{x}^{T}A = \overline{\lambda}\overline{x}^{T}\]
So, we can get
\[\overline{\lambda}\overline{x}^{T}x = \overline{x}^{T}Ax = \overline{x}^{T}\lambda x=\lambda \overline{x}^{T}x\]
Since $x \neq 0$,
\[\overline{x}^{T}x = \overline{x}_{1} \cdot x_{1} + \overline{x}_{2} \cdot x_{2} + \cdots +  \overline{x}_{n} \cdot x_{n} > 0\]
So, we can get $\overline{\lambda} = \lambda$ from $\overline{\lambda}\overline{x}^{T}x = \lambda \overline{x}^{T}x$, which means $\lambda$ is real.

:::

- Form the matrices $P$ and $S$ in R and use the syntax *eigen(A)$values* to find their eigenvalues. (According to the result we proved, $S$ should have real eigenvalues and $P$ might or might not have real eigenvalues). 
$$P = \begin{pmatrix} -4&5&6\\1&0&9 \\9&1&2\end{pmatrix}
\qquad
S = \begin{pmatrix} -1&2&1\\2&7&-3\\1&-3&4\end{pmatrix}
$$

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px"}

**Solution**:

```{r}
P <- matrix(c(-4, 1, 9, 5, 0, 1, 6, 9, 2), nrow = 3, ncol = 3)
S <- matrix(c(-1, 2, 1, 2, 7, -3, 1, -3, 4), nrow = 3, ncol = 3)
print(eigen(S)$values)
print(eigen(P)$values)
```

:::

### Q2: Nearly R-O
Write some code to create and print out this matrix (it's possible to do it in two lines, but any solution is fine as long as you don't separately type all 16 entries). Explain why it is nearly a R-O matrix, where "R-O" stands for something on our first-day slides. 
$$ 
A = \begin{pmatrix}
1&3&5&10\\
10&30&50&100\\
-2&-6&-10&-20\\
100&300&4&4
\end{pmatrix}
$$

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px"}

**Solution**:

```{r}
x <- c(1, 10, -2, 100)
A <- matrix(c(x, 3*x, 5*x, 10*x), nrow = 4, ncol = 4)
A[4, 3:4] <- 4
print(A)
```

:::

### Q3: Basic graph example
Write some code to plot the quadratic function $y=x^2 - 5x + 2$. Make sure that the minimum is visible inside your figure.  

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px;"}

**Solution**:

```{r}
library(ggplot2)


sigmoid <- function(x) x**2-5*x+2
x<-seq(-10, 15, by=0.01)
y<-sigmoid(x)
df<-data.frame(x, y)

g <- ggplot(df, aes(x,y)) +
  geom_line(col='red') +
  geom_hline(yintercept = 0.5) + 
  geom_vline(xintercept = 0) +
  ggtitle("sigmoid")
g
```

:::




### Q4: When power functions look linear
Consider the three graphs that the following code produces. *Note: I don't need to see the graphs in the version you turn in.  Please put "echo=FALSE" on line 60 once you finish looking at the graphs.*

```{r, echo=FALSE, include=FALSE}
x = 1:1000
y = x^(-2.0)
plot(x,y)
plot(log10(x), log10(y))
plot(x,y,log="xy")
```

Comment carefully on the differences you see between the three versions. Then explain why a function of the form $y = x^p$ looks linear on a log-log plot. *Hint: let $w = \log_{10}(y)$ and let $t = \log_{10}(x)$, then show that there is a linear relationship between $t$ and $w$.*

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px;"}

**Solution**:

In the first version, which is the original dot plot of function $y = x^{-2}$, the x-axis ranges from 1 to 1000, and y-axis ranges from 0 to 1.

In the second version, we manually change the x-axis and y-axis into $log_{10}(x)$ and $log_{10}(y)$, the plot shows the fucntion $y = -2x$. In this plot, the X range is also from 1 to 1000, in other words, $log_{10}(x)$ ranges from 1 to 3, and $log_{10}(y)$ ranges from -6 to 0.

In the third version, we can see although it looks like the same as the second plot, however, this plot does not show the funtion $y=-2x$, instead it shows $y = x^{-2}$. The reason it looks similar to the second one is that both the axises are all logarithmic through the code "log='xy'", it exists dramatic difference in the x-axis and y-axis. 


**Proof:**

Let $w= log_{10}(y)$, $t=log_{10}(x)$.

We can get 
\[y = x^{p} = (10^{t})^{p} = 10^{tp} = 10^{w}\]
Thus, $w = tp$, which is a linear relationship between $w$ and $t$.

:::


### Q5: Create a letter
As on the Day 1 activity, create a color image showing the first letter of your name by building appropriate matrices in R. Give it a white background (initialize the matrices with 1's instead of 0's). Add it to the Google Doc, and also include it here.

::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px; margin:10px;"}

**Solution**:

```{r}
library('magick')
myRed <- matrix(1,500,500) # a 500x500 grid of zeros
myRed[0:500,0:500] <- 1 # change some entries into ones

myGreen <- matrix(1,500,500)
myBlue <- matrix(1,500,500)
shiftleft <- 100
shiftDown <- 100
for (x in 0 : 100) {
  for (t in 0 : 50) {
    t <- t - shiftleft
    myGreen[x+shiftDown, 400+x+t] <- 0
    myRed[x+shiftDown, 400-x+t] <- 0
    myBlue[100+x+shiftDown, 300+x+t] <- 0
    myBlue[195+x+shiftDown, 395+x+t] <- 0
    myRed[395-x+shiftDown, 395+x+t] <- 0
    myGreen[395-x+shiftDown, 395-x+t] <- 0
  }

}
data <- array(c(myRed,myGreen,myBlue),dim = c(500,500,3))

im <- image_read(data) 
print(im) # this displays the image in RStudio and knitted documents
image_write(im,"mycolors.png")
```
:::

### Q6: High contrast image
The image "Department.png" is a cropped version of a photo by Stefani Reynolds in a January 2023 article about the upcoming US debt ceiling crisis in the New York Times. It shows part of the Treasury Department building in Washington. It is a color image, but it looks pretty gray because for most pixels, the values in the R, G, and B channels are all close together. Save the image in the same folder as your main RMD file and then uncomment these lines to see it: 

```{r}
library("magick")
a = image_read("Department.png")
A = as.integer(a[[1]])/256
redA = A[,,1]
greenA = A[,,2]
blueA = A[,,3]
print(a) # this displays the image in RStudio and knitted documents
```

We will make a high-contrast version of this image using a new code trick: updating a matrix or vector using conditional tests. 

Here is a first example where we create a vector and then ask which entries are less than 5:
```{r}
v <- 1:8
print(v)
print(v < 5)
```
The useful trick is that you can update the entries for which the condition is true: 
```{r}
v[v<5] <- -1
print(v)
```

The same trick works for matrices and high-dimensional arrays: 
```{r}
a <- matrix(rnorm(12),3,4) # create a 3x4 matrix with normally distributed entries
a[a<0] <- 0 # set all negative elements to be zero
print(a) # we should see about half zeros, half positive numbers
```

The three matrices redA, greenA, and blueA contain numbers between 0 and 1. Pick a cutoff between 0 and 1 (0.5 is a good choice but you can experiment) and then set all entries to 1 if they're greater than the cutoff, or 0 otherwise. Then display the altered image, the "high contrast" version. It should be mostly black-and-white but there will be some colored pixels - explain why. 


::: {style="border-style:solid; border-width:2px; border-color:black; padding:10px;margin:10px;"}

**Solution**:

```{r}
library("magick")
a = image_read("Department.png")
A = as.integer(a[[1]])/256
redA = A[,,1]
print(dim(redA))
greenA = A[,,2]
blueA = A[,,3]
redA[redA < 0.5] <- 0
redA[redA >= 0.5] <- 1
greenA[greenA < 0.5] <- 0
greenA[greenA >= 0.5] <- 1
blueA[blueA < 0.5] <- 0
blueA[blueA >= 0.5] <- 1
result <- image_read(array(c(redA,greenA,blueA), dim = c(382,370,3)))
print(result) # this displays the image in RStudio and knitted documents
```

In the image, we can find most of the pixels are black or white, but there still exist some pixels with colors. When we change the numbers in the three matrices, the number will be 0 or 1. So when we got (0, 0, 0), the color will be black and when we got (1, 1, 1), the color will be white. However, when there just exist one 1 or two 1s, for example (1, 1, 0) or (1, 0, 0), the pixel will have other colors, yellow or red.
:::

